Analyzing Arrest Patterns and Racial Representation in Toronto

### 2024-09-26 paper/paper.qmd
Checking and improving introduction and abstract
Fixing suggestions made by peers

## Total number of arrests by age group for the year 2020 and 2021

@@

## Arrests by Ethnic and Identity-Based Groups for Year 2020 and 2021

@@

However, it is worth highlighting that the Black population had the highest number of individuals booked after arrest in both 2020 and 2021.

@@

## Number of Arrests by Age Group for the year 2020-2021

As depicted in [@fig-fig3], the data reveals a non-uniform distribution of arrests across age groups. The 25 to 34 and 35 to 44 age groups had the highest number of arrests in both 2020 and 2021. Additionally, the data indicates a notable decrease in arrests for these two age groups between 2020 and 2021. In contrast, other age groups experienced an increase in arrests during the same period, indicating differing trends across age demographics.

@@

>>>>

## Total number of arrests by age group for the year 2020 and 2021 {#sec-Age}

@@

## Arrests by Ethnic and Identity-Based Groups for Year 2020 and 2021 {#sec-eth}

@@

However, it is worth highlighting that the Black population had the highest number of individuals who were booked after arrest in both 2020 and 2021.

@@

## Number of Arrests by Age Group for the year 2020-2021 {#sec-group}

An analysis of arrests by age groups is essential to understanding the demographic patterns of law enforcement activity. [@fig-fig3] illustrates the distribution of arrests across different age groups for the years 2020 and 2021. The age groups included in the dataset are Under 17, 18 to 24 years, 25 to 34 years, 35 to 44 years, 45 to 54 years, 55 to 64 years, and 65 years and over.

The data reveals a non-uniform distribution of arrests across age groups, with 25 to 34 and 35 to 44 age brackets accounting for the highest number of arrests in both 2020 and 2021. However, there is a notable decrease in the number of arrests for these age groups of 2020 to 2021 which indicates that there may be a possible shift in law enforcement activity.

In contrast, the other age groups experienced an increase in arrests during the same period. In particular, the number of arrests for individuals aged 18 to 24 and 45 to 54 saw an upward trend from 2020 to 2021.

@@

In [@sec-Age], the analysis highlights that arrests are not evenly distributed across age groups, with certain age ranges, particularly individuals aged 25 to 44, being more likely to be arrested during the study period. These findings suggest that certain demographic factors related to age may influence interactions with law enforcement. Further exploration is required to understand the socio-economic, behavioral, and legal factors that contribute to the higher arrest rates among individuals in their mid-20s to mid-40s.

In [@sec-eth] the data suggests that there are notable disparities in arrest rates across different ethnic groups, with Black and Indigenous populations being of particular concern.

In [@sec-group] the findings suggest that law enforcement practices or external factors influencing crime rates may vary significantly across age groups.

However, none of these findings can definitively point to systemic bias without further context, particularly around socio-economic factors and community-specific conditions.
